\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate, url}
\newcommand{\dx}{dx}
\begin{document}

% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Bonus Homework and Exam Review - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Due Friday, December 9 at the start of the final exam.}
\end{center}

{\bf It is strongly recommended that you do as many of these problems as possible. This is the best
way to review for the exam.} I recommend the following: Work on ten problems at a time, and come up
with solutions without checking the book or your notes. Take a break. Then, look at your solutions
and compare them to the book, your notes, and your old homeworks and see if there is anything you want
to change.

{\bf For any graphing problems:} Find all critical points, inflection points, intervals of increase
and decrease, where the graph is concave up or down, and horizontal and vertical asymptotes.

{\bf Where appropriate:} Always draw a diagram and/or a graph if it is relevant to your problem,
and explain yourself clearly.

{\bf The exam will include}, among other questions: at least one graphing question, at least
one optimization question, at least one related rates question, at least one volume or area
question, at least one question where you are given a graph and have to say something about it,
and at least one of the first eight questions below. 

{\bf Extra credit: This assignment is completely optional.} 
It is worth extra credit equivalent to two homework assignments.
{\bf Partial extra credit cheerfully given}; this is {\itshape extremely long}, 
if you get through part of this, please turn in
what you have.

{\bf Good luck!} Taylor, Lauren, and I are all here to help if you get stuck.

\begin{enumerate}[(1)]

\item
Give the definition of the derivative of a function 
$f(x)$ at the point $x = a$. (Please give an algebraic
definition, using an equation.) Draw a picture and
explain why your equation gives the slope of the tangent
line to the graph of $f(x)$ at $x = a$.

\item
Give the definition of the definite integral of a function
$f(x)$ between $x = a$ and $x = b$. (Give an
algebraic definition, using an equation.)
Draw a picture and explain why your equation
gives the area under the graph of $f(x)$ between
$a$ and $b$.

\item
Give the definition of the indefinite integral
of a function $f(x)$.

\item
What do indefinite integrals have to do with derivatives, and how do you
know?

\item
What do definite integrals have to do with derivatives, and how do you know?

\item
State both parts of the Fundamental Theorem of Calculus.

\item
The first part of the Fundamental Theorem of Calculus tells you that
$\frac{d}{dx}\bigg( \int_a^x f(t) dt \bigg) = f(x)$. Why is this
true? Draw a picture and explain.

\item
What does the Mean Value Theorem say? Draw a picture and explain.

\item
Find the absolute maximum and minimum of $f(x) = x e^{-x^2/8}$ on the interval $[-1, 4]$.

\item
If $f$ and $g$ are two functions, draw a picture which explains why $(fg)' = f' g + g' f$.

\item
A snowball melts so that its surface area decreases at a rate of 1 $cm^2/min$. Find the rate
at which the diameter decreases when the diameter is 10 cm. (The surface area of a sphere of radius
$r$ is $4 \pi r^2$.

\item
Find the absolute maximum and minimum values of $f(x) = \frac{x}{x^2 + 1}$ on $[0, 2]$.

\item
Give an equation of a function which is not differentiable (at at least one point), and
explain why it is not differentiable.

\item
Do prob. 7 on p. 285 of Stewart.

\item
Find $f'(t)$ if $f(t) = \frac{1}{2} t^6 - t^4 + t$.

\item
Define the function $\cos(x)$.

\item
A man starts walking north at 4 ft/s from a point $P$. Five minutes later a woman starts
walking south at 5 ft/s from a point 500 ft due east of $P$. At what rate are they moving apart
15 min after the woman starts walking?

\item
Do prob. 3 on p. 162 of Stewart.

\item
Verify that $f(x) = \sqrt{x} - x/3$ satisfies the hypotheses of Rolle's thorem
on the interval $[0, 9]$. Then find all numbers $c$ that satisfy the conclusion of Rolle's
theorem.

\item
Find the absolute maximum and minimum of $f(t) = 2 \cos t + \sin 2t$ on the interval
$[0, \pi/2]$.

\item
Do prob. 6 on p. 162 of Stewart.

\item
Graph a function $f$ for which $f(0) = 0$, $f(1) = 1$, $\lim_{x \rightarrow \infty} f(x) = 0$,
and $f$ is odd.

\item
Find all local and absolute maxima and minima of $f(x) = e^x$.

\item
Find $\int_0^4 \sqrt{4x - x^2}$ using geometry.

\item
Find $f'(u)$ if $f(u) = \frac{\ln u}{1 + \ln(2u)}$.

\item
Find the derivative of $f(x) = \sqrt{1 + 2x}$ using the definition of the derivative.
State the domain of $f(x)$ and of its derivative.

\item
Do prob. 9 on p. 97 of Stewart.

\item
Do prob. 61 on p. 297 of Stewart.

\item
Graph the function $y = x^3$ on $[0, 1]$ and estimate the area under the curve
by dividing it into four intervals.


\item
Find the first and second derivatives of $G(r) = \sqrt{r} + r^{1/3}$.

\item
What does $\lim_{x \rightarrow -\infty} g(x) = 6$ mean?

\item
Find $y'$ if $y = x^x$.

\item
Explain why $\frac{d}{dx}(\ln x) = \frac{1}{x}$. (You may use any fact you know
about the function $y = e^x$.

\item
A Norman window has the shape of a rectangle with a semicircle on top.
If the perimeter of the window is 30 ft, find the dimensions of the window
with the largest area.

\item
Graph $f(x) = e^{-x^2}$.

\item
Find $\lim_{x \rightarrow 16} \frac{4 - \sqrt{x}}{16 x - x^2}$.

\item
Find $y'$ if $y= \frac{x + 1}{x^3 + x - 2}$.

\item
If $f(x) = 3x^2 - 5x$, find $f'(2)$ and use it to find an equation of the tangent
line to the parabola $y = 3x^2 - 5x$ at the point $(2, 2)$.

\item
Do prob. 52 on p. 345 of Stewart.

\item
Find the derivative of $f(t) = 5t - 9t^2$ using the definition of the derivative.
State the domain of the function and of its derivative.

\item
Sketch the graph of a function with two local maxima, one local minimum, and no
absolute maximum.

\item
Do prob. 4 on p. 388 of Stewart.

\item
Find $g'(x)$ if $g(x) = \frac{3x - 1}{2x + 1}$.

\item
Find the area bounded by the curves $y = 1/x$, $y = 1/x^2$, and $x = 2$.

\item
Graph $f(x) = \frac{x}{x - 1}$.

\item
If $\sqrt{xy} = 1 + x^2 y$, find $\frac{dy}{dx}$. (Your answer may have $y$ in it.)

\item
Find $\lim_{x \rightarrow - \infty} \frac{1}{2x - 3}$.

\item
Do prob. 42 on p. 164 of Stewart.

\item
A farmer wants to build a rectangular fence along a river. She has 100 feet of fencing and
does not need any fence along the river. How much area can she enclose?

\item
Find the limit $\lim_{x \rightarrow -2} \frac{2 - |x|}{2 + x}$ if it exists.
If it does not exist, say why.

\item
Evaluate $\int_0^1 10^x dx$.

\item
A boat leaves a dock at 2:00 and travels due south at 20 km/h. Another boat has been
heading due east at 15 km/h and reaches the same dock at 3:00. At which time were the two
boats closest together?

\item
Find the volume of the solid obtained by rotating the region bounded by
$y = 1/x$, $x = 1$, $x = 2$, $y = 0$ about the $x$-axis.

\item
Let $f(x) = x^2$. Use the Mean Value Theorem to show that there is a point $c \in (-1, 2)$
with $f'(c) = 1$. Then, find $f'(x)$ and figure out all such values of $c$. Draw
a picture which illustrates your conclusions.

\item
Explain why $\frac{d}{dx}(\cos x) = - \sin x$.

\item
Find the derivative of $f(x) = \csc x$ and $g(x) = \sec x$.

\item
Find the volume of a square pyramid with base length $b$ and height $b$.

\item
Find the point on the line $y = 4x + 7$ that is closest to the origin.

\item
Find $\lim_{x \rightarrow \infty} \big( \sqrt{9 x^2 + x} - 3x \big)$.

\item
If $1 + x = \sin(x y^2)$, find $\frac{dy}{dx}$. (Your answer may have $y$ in it.)

\item
Find the volume of a sphere with radius $r$.

\item
A rectangular storage container with an open top is to have a volume of
10 $m^3$. The length of its base is twice the width. Material for the base
costs 10 dollars per square meter. Material for the sides costs 6 dollars per square
meter. Find the cost of materials for the cheapest such container.

\item
Find the volume of the solid obtained by rotating the region bounded by the following
curves about the $y$-axis: $y^2 = x$, $x = 2y$.

\item
Graph $f(x) = \frac{x}{x^2 + 9}$.

\item
You drive 120 miles from Columbia to Charlotte, and the trip takes two hours.
At some point, your speed is exactly 60 mph. Explain how you know this. Must there
be a point at which your speed is exactly 65 mph?

\item
The number of bacteria after $t$ hours in a laboratory experiment is $n = f(t)$.
What is the meaning of the derivative $f'(5)$? What are its units?

Suppose there is an unlimited amount of space and nutrients for the bacteria.
Which do you think is larger, $f'(5)$ or $f'(10)$? Does it matter if the supply of
nutrients is limited? Explain.

\item
Do prob. 7 on p. 410 of Stewart.

\item
Explain why $\lim_{\theta \rightarrow 0} \frac{ \sin \theta}{\theta} = 1$ without
L'Hospital's rule.

\item
Graph $y =  x \sqrt{5 - x}$.
 
\item
Find the limit $\lim_{t \rightarrow 9} \frac{9 - t}{3 - \sqrt{t}}$.

\item
Find $\frac{dy}{dx}$ if $y = \sin^{-1} x$.

\item
Evaluate $\int_0^1 x e^{-x^2} dx$.

\item
A television camera is positioned 4000 ft from the base of a rocket launching pad.
A rocket rises vertically, and its speed is 600 ft/s when it has risen 3000 feet.
How fast is the distance from the television camera to the rocket changing at that moment?

\item
Find two numbers whose sum is 10 and whose product is a maximum.

\item
Find $\lim_{x \rightarrow \infty} \cos x$.

\item
Graph $y = x \tan x$ for $ - \pi/2 < x< \pi/2$.

\item
Gravel is being dumped from a conveyor belt at a rate of 30 $ft^3/min$, and it forms
a pile in the shape of a cone whose base diameter and height are always equal. How fast is the pile
increasing when the pile is 10 ft high?

\item
You and nine friends are working on calculus problems together. Each of you can solve
problems at a rate of $r(t) = 6 + t$, where $t$ is the number of hours you have worked
(you improve as you go along!), and $r(t)$ is the number of calculus problems per hour.

If each problem takes half a page, and you work front and back, and a piece of paper
is 0.01 in thick, how fast is the pile of homework problems increasing when you have
been working for 35 hours?

\item
Evaluate $\int \frac{\sin 2x}{\sin x} dx$.

\item
Evaluate $\int_0^7 \sqrt{4 + 3x} dx$.

\item
Graph $y = x/2 - \sin x$ for $0 < x < 3 \pi$.

\item
A parking lot charges \$5 for the first hour (or part of an hour) and \$5 for
each succeeding hour (or part), up to a daily maximum of \$20. Sketch a graph
of the cost of parking at this lot as a function of the time parked there.
In addition, discuss the discontinuities of this function and their significance
to someone who parks in the lot.

\item
Find all points on the graph of the function $f(x) = 2 \sin x + \sin^2 x$ at which
the tangent line is horizontal.

\item
Find $y'$ if $y = \frac{1 - \sec x}{\tan x}$.

\item
Find the horizontal and vertical asymptotes of $y = \frac{x^3 - x}{x^2 - 6x + 5}$.

\item
Evaluate $\int \cos \theta \sin^6 \theta d \theta$.

\item
Graph $y = x - \ln x$.

\item
A lighthouse is on a small island 3 km away from the nearest point $P$ on a straight
shoreline and its light turns four revolutions per minute. How fast is the beam of light
moving along the shoreline when it is 1 km from $P$?

\item
Find the derivative of $y = (2x - 5)^4 (8 x^2 - 5)^{-3}$.

\item
Evaluate $\int e^x \sin(e^x) dx$.

\item
A trough is 10 ft long and its ends have the shape of isoceles traingles that
are 3 ft across the top and have a height of 1 ft. If the trough is being filled with
water at a rate of 12 $ft^3/min$, how fast is the water level rising when the water
is 6 inches deep?

\item
Graph $y = 1/(1 + e^{-x})$.

\item
Explain what it means to say that $\lim_{x \rightarrow 1^-} f(x) = 3$ and
$\lim_{x \rightarrow 1^+} f(x) = 7$. In this situation is it possible that
$\lim_{x \rightarrow 1} f(x)$ exists?

\item
A ball is thrown into the air with velocity 40 ft/s, and its height in feet after
$t$ seconds is given by $y = 40t - 16t^2$. Find the velocity when $t = 2$.

\item
Evaluate $\int x \sin(x^2) dx$.

\item
Find the equation of the tangent line to $y = \frac{1}{\sin x + \cos x}$ at the point
$(0, 1)$.

\item
Find the derivative of $f(x) = (1 + 2x + x^3)^{1/3}$.

\item
Graph $y = \frac{x^2 - 4}{x^2 - 2x}$. (Hint: look for a partial shortcut)
\item
Do prob. 17 on p. 151 of Stewart.

\item
Find $\lim_{\theta \rightarrow 0} \frac{\tan 6 \theta}{\sin 2 \theta}$.

\end{enumerate}

\end{document}
