\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Homework 4 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Due Monday, September 24}
\end{center}
\begin{enumerate}[(a)]

\item
Draw a graph of a function which is not differentiable, and geometrically explain why it is not differentiable.

\item
Give an equation of a function which is not differentiable, and algebraically explain why it is not differentiable.
(You can use the same function or a different function.)

\item
Give the definition of the {\itshape derivative} of a function
$f(x)$ at the point $x = a$. (Please give the algebraic definition,
using an equation.)

Draw a picture and explain why your
equation gives the slope of the tangent line to the graph of $f(x)$
at $x = a$.

\item
Stewart, Ch. 2.8, 3, 5-8, 14.
\item
Stewart, Ch. 2.8, 19-29 (even).
\item
Stewart, Ch. 2.8, 41-43.
\item
If $f(x) = c$, where $c$ is a constant, find $f'(x)$ using the definition.
Draw a picture which explains your conclusion.

\item
Explain why the derivative of $e^x$ is equal to $e^x$. You may take for granted that
$\lim_{h \rightarrow 0} \frac{e^h - 1}{h} = 1$.

\item
Stewart, Ch. 3.1, 2-14, 27-36, 45-46 (even).

\item
Stewart, Ch. 3.1, 49. (Note: The acceleration is the derivative of the velocity.)

\item
What is the 500th derivative of $f(x) = x^{100}$? Explain why.

\item
Stewart, Ch. 3.2, 1-18, 27-30 (even).

\item
Stewart, Ch. 3.2, 31-34 (even).
\end{enumerate}
Additional problems:

\begin{enumerate}[(a)]
\item
Stewart, Ch. 2.8, 15-16 (all), 19-29 (odd).

\item
Stewart, Ch. 3.1, 2-14, 27-36, 45-46 (odd).

\item
Stewart, Ch. 3.2, 1-18, 27-30 (odd).

\item
Stewart, Ch. 3.2, 31-34 (odd).
\end{enumerate}
{\bf Bonus} (1 point each):
\begin{enumerate}[(a)]
\item
Evaluate $\lim_{x \rightarrow 1} \frac{x^{2012} - 1}{x - 1}.$
\item
Find the tenth derivative of $f(x) = x^2 e^x$. (Hint: This is way too messy
to do by brute force. Find a pattern.)
\end{enumerate}
\end{document}
