\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Examination 2 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Wednesday, October 31, 2011}
\end{center}

There will be seven questions, all of them taken from the homework
assignments. The last two will definitely appear, and five of the first ten
will appear, chosen at random.

As before, the ``additional'' problems on the homeworks are fair game.

\begin{enumerate}[(1)]
\item
One problem from (a)-(d), (i) or Section 3.3 on Homework 5, selected at random.

\item
One problem from (j) or Section 3.4 on Homework 5, selected at random.

\item
One problem from (l), (m), (o), or Section 3.5 on Homework 5, selected at random.

\item
One problem from (a)-(d) or Section 3.6 on Homework 6, selected at random.

\item
One problem from Section 3.7 on Homework 6, selected at random.

\item
Problem (i), (j), or (k) on Homework 6, selected at random.

\item
One problem from Section 3.8 on Homework 6, selected at random.

\item
One problem from Section 3.9 on Homework 7, selected at random.

\item
One problem from (b)-(e) or Section 4.1 on Homework 7, selected at random.

\item
One problem from Chapter 4.3 on Homework 8, selected at random.

\item
One problem from Chapter 3 Review on Homework 7 (additional), selected at
random.

\item
One problem from Chapter 4.5 or (f)-(j) on Homework 8, selected at random.


\end{enumerate}

\end{document}
