\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Practice Examination 1 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Wednesday, September 14, 2011}
\end{center}

Please work without books, notes, calculators, or any assistance from others. If you have
any questions, feel free to ask me. 

Please do your work on separate paper; you should staple this sheet to your work (put this on top)
and turn in everything together. 
\\
\\
\begin{enumerate}[(1)]
\item
Graph the function $y = \sqrt{x + 3}$, not by plotting points, but by
starting with the graph of $y = \sqrt{x}$ and applying the appropriate transformations.
(Be sure to explicitly explain your work.)

\item
Define the term {\itshape inverse function}. Give an example of a function that
has an inverse, and of a function that does not.

\item
Evaluate $$\lim_{x \rightarrow 2} \frac{x^2 + x - 6}{x - 2},$$
if the limit exists.

\item
A parking lot charges three dollars for the first hour (or part of an hour)
and two dollars for each succeeding hour (or part), up to a maximum of ten dollars.

(a) Sketch a graph of the cost of parking at this lot as a function of the time parked
there.
(b) Discuss the discontinuities of this function and their significance to someone
who parks in the lot.

\item
Evaluate $$\lim_{x \rightarrow -4} \frac{ \sqrt{x^2 + 9} - 5}{x + 4},$$
if the limit exists.

\item
The cost of producing $x$ ounces of gold from a new gold mine is $C = f(x)$ dollars.

(a) What is the meaning of the derivative $f'(x)$? What are its units?

(b) What does the statement $f'(800) = 17$ mean?

(c) Do you think the values of $f'(x)$ will increase or decrease in the short term?
What about the long term? Explain.

\item
Evaluate
$$\lim_{x \rightarrow \infty} \bigg( \sqrt{9x^2 + x} - 3x \bigg).$$

\item
If $f(x) = 3 - 2x + 4x^2$, find $f'(a)$.

\end{enumerate}

\end{document}
