\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate, url}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Supplementary Evaluation - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
\end{center}

Answering this is not required, but it will be very helpful next time I teach Math 141. If you fill
out this evaluation, please return it to my mailbox outside LeConte 411. Thank you!

\begin{enumerate}[(1)]
\item
Did you ever have any difficulty hearing my voice, reading the blackboard, or anything related?
(If yes, please explain.)

\vskip 1in
\item
{\bf Homework:} Did you ever spend more than 8-10 hours during any one week on the homework? Consistently?
(It was intended that you should not have to.) If so, please elaborate.

\vskip 2in
\item
Was the homework helpful for your understanding of the material? Please comment on any parts of the homework
assignments which were particularly helpful or unhelpful.
\newpage
\vskip 2in
\item
{\bf Choice of topics:} Next time, I intend to make a few minor changes:

\begin{itemize}
\item
Add a lecture near the beginning reviewing ``word problems'' and how to approach them
\item
Remove the
lecture on the ``limits game'' and the formal definition of a limit
\item Expand the treatment of related
rates substantially
\item (Maybe) remove the discussion of logarithmic differentiation
\item (Maybe) say a little
bit about exponential growth and decay (see Section 3.8).
\end{itemize}
Do you agree with these changes? Do you suggest any others?

\vskip 2in
\item
Did you ever have any difficulty contacting me or other instructional staff? If yes, please elaborate.

\vskip 1in
\item
(I very much hope the answer to this question is no, but if yes, please explain.) Do you ever feel you were
treated unfairly for any reason?

\vskip 1in
\item
Do you have any other suggestions for the next time I teach Math 141?
\end{enumerate}

\end{document}
