\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate, url}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Homework 10 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Due Friday, October 28}
\end{center}

{\bf Credits:} Some questions are taken from Arun Ram's calculus notes; see
\url{http://www.ms.unimelb.edu.au/~ram/Teaching/2006Fallmath221/HW8F06.pdf}

For all the graphing problems, explicitly describe each of the following when relevant
to your graph.

\begin{enumerate}[(1)]
\item
Where are the $x$- and $y$-intercepts?

\item
Where is the graph positive and negative?

\item
Where are the critical points?

\item
Where is the graph increasing and decreasing?

\item
Where are the inflection points?

\item
Where is the graph concave up and concave down?

\item
Where are the asymptotes? (If $f(x)$ has asymptotes)
\end{enumerate}

\begin{enumerate}[(a)]
\item

Stewart, Ch. 4.5; 1-14, 25-38, 41-48; even required, odd recommended.

\item
Graph $f(x) = 2 \cos x + \sin 2x$.

\item
Graph $f(x) = 2 \sin x + \cos 2x$.

\item
Graph $f(x) = e^{-x}$.

\item
Graph $f(x) = e^{-x^2}$.

\item
Graph $f(x) = \ln(4 - x^2)$.

{\bf Related rates warmup questions}. These exercises don't involve any calculus. For each of
them, write an equation which relates the two expressions described. Be sure to {\bf draw a picture}
and {\bf explain what your variables stand for}.

{\bf Note:} A couple of the questions contain {\itshape red herrings:} information which
is not needed to answer the question.

\item
Relate the area of a circle to its diameter.

\item
Relate the volume of a cylinder of radius 1 to its height.

\item
The bottom of a rectangular swimming pool is $30 \times 50$ feet. Relate
the depth of the water in the pool to its volume.

\item
A woman is standing at some distance from a 20 foot tall pole. A streetlight
is on top of the pole. Relate the length of her shadow to the distance between
the woman and the height of the pole.

\item
A lighthouse is on a small island 3 km away from the nearest point $P$ on 
a straight shoreline and its
light turns four revolutions per minute. Relate the position of the light
on the shoreline to the direction of the light.

\item
A 10 foot ladder rests on a wall and is sliding down the wall (and the bottom is sliding away from the wall). 
Relate the angle between the top of
the ladder and the wall, and the height of the top of the latter.

\item
In the previous question, relate the height of the top of the latter to the distance of
the bottom of the ladder from the wall.

\item
A television camera is positioned 4000 ft from the base of a rocket launching
pad. A rocket rises vertically. Relate the distance between the rocket and the
camera to the height of the rocket.

\item
In the previous question, relate the camera's angle of elevation to the
height of the rocket.

\item
A man starts walking north at 4 ft/s from a point $P$. Five minutes
later a woman starts walking south at 5 ft/s from a point 500 ft due
east of $P$. Relate the distance between the man and the woman and
the time the man has been walking.

\item
In the previous problem, relate the distance between the man and the 
woman and the time the woman has been walking.

\item
In the previous question, relate the distance between the man and the
woman and the distance travelled by the man.

\end{enumerate}

\end{document}
