\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate, url}
\newcommand{\dx}{dx}
\begin{document}

% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Homework 12 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Due Friday, November 11}
\end{center}

\begin{enumerate}[(a)]
\item
What is an indefinite integral? Explain thoroughly.

\item
What is a definite integral? Explain thoroughly and draw a picture.

\item
Graph the function $y = x^2$, and estimate $\int_0^1 x^2 dx$ by dividing
$[0, 1]$ into four, then six, then eight intervals.

\item
Graph the function $y = x^3$ and estimate $\int_0^1 x^3 dx$ by dividing
$[0, 1]$ into two, three, four intervals.

\item
Graph the function $y = x$ and estimate $\int_0^1 x dx$ by dividing
$[0, 1]$ into four, then six, then eight intervals. Then, evaluate $\int_0^1 x dx$
using geometry and compare your answers.

\item
Evaluate $\int_0^4 \sqrt{4 - (x - 2)^2} \dx$ using geometry.

\item
Evaluate $\int_0^4 \sqrt{4x - x^2} \dx$ using geometry.

\item
Evaluate $\int_0^3 4x \dx$ using geometry.

\item
Evaluate $\int_{-2}^0 3x \dx$ using geometry.

\item
Evalute $\int_{-4}^4 \frac{x}{2} \dx$ using geometry.

\item
Evaluate $\int_{-2}^5 (x + 3) \dx$ using geometry.

\item
What does the Fundamental Theorem of Calculus say, and why is it true? Explain carefully
and throughly.

\item
Stewart, Ch. 4.9, 49-52, 57, 63. (Recall that the velocity function is the derivative
of the position function, and the acceleration is the derivative of the velocity. In 63,
use $a(t) = -10 m/s^2$.)

\item
Stewart, Ch. 5.3, 4, 7, 8.

\item
Stewart, Ch. 5.3, 19-40 (omit 34); even required, odd recommended.

\item
Stewart, Ch. 5.3, 43.

\item
Stewart, Ch. 5.4, 9-18 (omit 13), 35-38; even required, odd recommended.

\end{enumerate}

\end{document}
