\documentclass[11pt]{article}
\textwidth 7.0in

\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Makeup Examination 3 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Friday, November 18, 2011}
\end{center}

Please work without books, notes, calculators, or any assistance from others. If you have
any questions, feel free to ask me. 
\\
\\
\begin{enumerate}[(1)]
\item
Verify that $f(x) = \frac{x}{x + 2}$ satisfies the conclusion of the Mean Value Theorem
on the interval $[1, 4]$, and find all numbers $c$ which satisfy the conclusion of the Mean
Value Theorem.

\item
Sketch the graph of $f(x) = \frac{1}{x^2 - 9}$. In addition, find the intervals of increase
and decrease, the local maximum and minimum values, the intervals of concavity, and the
inflection points.

\item
The graph of the derivative $f'$ of a continuous function $f$ is shown. Sketch a graph of
$f$ between $x = 0$ and $x = 4$, given that $f(0) = 0$. Label any local maxima or minima
and inflection points. (You may ignore the part of the curve with $x > 4$.)

\item
Find two numbers whose difference is 10 and whose product is a minimum.

\item
Two cars start moving from the same point. One travels south at 60 mi/h and the other
travels west at 25 mi/h. At what rate is the distance between the cars increasing two
hours later?

\item
Evaluate
$\int_{-2}^0 3x dx$ using geometry.

\item
Evaluate
$$\int e^{\cos t} \sin t dt.$$

\end{enumerate}

\end{document}
