\documentclass[11pt]{article}
\textwidth 7.0in

\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Practice Examination 2 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Wednesday, October 12, 2011}
\end{center}

Please work without books, notes, calculators, or any assistance from others. If you have
any questions, feel free to ask me. 

The exam will have only eight questions. This has nine.
\\
\\
\begin{enumerate}[(1)]
\item
Do problem 8 on p. 162 of Stewart. (On an actual exam, any pictures will be photocopied
or hand-drawn in.)

\item
If $f(x) = x + \sqrt{x}$, find $f'(x)$ using the definition of the derivative.

\item
Find $\frac{dy}{dx}$ if $y = \frac{x^2 - 2 \sqrt{x}}{x}$.

\item
Find $\frac{dy}{dx}$ if $y = \csc x$. (You may take the derivatives of $\sin x$ and $\cos x$
for granted.)

\item
Find $\frac{dy}{dx}$ if $y = \sec^2 x + \tan^2 x$.

\item
If $e^{x/y} = x - y$, find $\frac{dy}{dx}$ by implicit differentiation.

\item
A water trough is 10 m long and a cross-section has the shape of an
isosceles trapezoid that is 30 cm wide at the bottom, 80 cm wide at the top,
and has height 50 cm. If the trough is being filled with water at the rate of
$0.2 \ m/\textnormal{min}^3$, how fast is the water level rising when the water
is 30 cm deep?

\item
Find $f'(x)$ if $f = \ln | \sec 5x + \tan 5x |$.

\item
Sketch the graph of a function that has two local maxima, one
local minimum, and no absolute maximum.


\end{enumerate}

\end{document}
