\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Final Examination - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Friday, December 9, 2011}
\end{center}

Please work without books, notes, calculators, or any assistance from others. If you have
any questions, feel free to ask me. 

There are sixteen questions, and you have three hours. {\bf It is extremely wise to take all
three hours.} I've showed you ways to check and reflect upon your work. Please use them!

As always, explain yourself clearly, show all your work, and draw pictures and/or graphs
where appropriate.
\\
\\
\begin{enumerate}[(1)]
\item
Give the definition of the derivative of a function $f(x)$ at the point $x = a$. (Please
give an algebraic definition, using an equation.) Draw a picture and explain why your
equation gives the slope of the tangent line to the graph of $f(x)$ at $x = a$.

\item
Give the definition of the definite integral of a function $f(x)$ between the points $x = a$
and $x = b$. (Please
give an algebraic definition, using an equation.) Draw a picture and explain why your
equation gives the area under the graph of $f(x)$ between $x = a$ and $x = b$.

\item
State both parts of the Fundamental Theorem of Calculus.

\item
Determine the limit, if it exists:
$$\lim_{x \rightarrow -4} \frac{ \sqrt{x^2 + 9} - 5}{x + 4}.$$

\item
If $f(x) = 3 - 2x + 4x^2$, find $f'(x)$ using the definition of the derivative.

\item
The figure below shows graphs of $f, \ f', \ f'', \ f'''$. Identify each curve, and explain
your choice.

\item
Find an equation to the tangent line to the curve $\sec(x)$ at the point $(\pi/3, 2)$.

\item
Find $\frac{dy}{dx}$ by implicit differentiation, given that
$$e^{x/y} = x - y.$$
\newpage
\item
Verify that the function $f(x) = e^{-2x}$ satisfies the conclusion of the Mean Value
Theorem on the interval $[0, 3]$. Then find all numbers $c$ that satisfy the conclusion
of the Mean Value Theorem.

\item
In this and the next question, find and identify on your graph the following:
the $x$- and $y$-intercepts; the critical points; where the graph is increasing and
decreasing; the inflection points; where the graph is concave up and concave down;
asymptotes (if any).

Graph $y = e^x/x$.

\item
Graph $y = x \sqrt{5 - x}$.

\item
A television camera is positioned 4000 ft from the base of a rocket launching pad.
A rocket rises vertically, and its speed is 600 ft/s when it has risen 3000 ft. How fast
is the camera's angle of elevation changing at this moment?

\item
Find an equation of the line through the point $(3, 5)$ that cuts off the least area
from the first quadrant.

\item
Evaluate
$$\int_0^2 x(2 + x^5) dx.$$

\item
Evaluate
$$\int_0^{\sqrt{\pi}} x \cos(x^2) dx.$$

\item
The region bounded by the equations $y = \frac{1}{4} x^2$ and $y = 5 - x^2$ is revolved around the $x$-axis.
Find the volume of the solid obtained.

(Be sure to draw a good sketch of this region, this solid, and a typical slice.)

\end{enumerate}

\end{document}
