\documentclass[14pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Examination 1 - Math 142, Frank Thorne (thorne@math.sc.edu)}
\end{center}
\begin{center}
{\bf Thursday, September 26, 2013}
\end{center}

{\bf Instructions and Advice:} 

\begin{itemize}
\item
There are seven questions. Each of them is essentially the same as one of the `required'
or `additional' problems from your homework, sometimes with minor changes.
\item
There is one question from each of Sections 5.5, 6.1, 7.1, 7.3, 7.4, 7.5, and 7.8,
with one exception. They appear in random order; it is up to you to determine the integration strategy for each integral.
\item
You are welcome to as much scratch paper as you need. Turn in everything you want graded,
and throw away everything you do not want graded.
\item
{\bf Draw pictures where appropriate.} For the area problem, graph the area to be computed
and draw a typical slice. If you do a trigonometric substitution, draw a triangle that
represents the substitution you make.

For definite integrals, it is recommended (but not required) that you draw a graph
representing the value of the definite integral, to allow you to check your work.
\item
Be clear, write neatly, explain what you are doing, and show your work. {\bf This is especially
important for earning partial credit} in case your work contains one or more mistake.
Be warned that {\bf work I cannot understand will not receive any credit.}
\item
75 minutes is a long time. Don't dilly-dally, but don't rush. {\bf You are strongly advised
to take the entire 75 minutes to complete the examination.} If you finish early, you have the
opportunity to check your work.
\item
Please work without books, notes, calculators, or any assistance from others. 
\item
I will be at the front of the room; if you have
any questions, feel free to ask me. 
\end{itemize}

\begin{center}
{\bf GOOD LUCK!}
\end{center}
\newpage

\begin{enumerate}[(1)]
\item
Evaluate
\[
\int \frac{x^2 + 2x - 1}{x^3 - x} dx.
\]
\item
Find the area bounded by the graphs of $y = x^2$ and $y = 12x - x^2$.

As part of your solution, draw both graphs and the area to be computed, and draw a typical
slice which represents what you are integrating. 
\item
Evaluate
\[
\int_1^{\infty} e^{-y/3} dy.
\]
\item
Evaluate
\[
\int_1^3 \frac{3t}{(t + 1)^2} dt.
\]
\item
Evaluate
\[
\int \frac{ \sqrt{t^2 - 1} }{t} dt.
\]
\item
Evaluate
\[
\int_1^e (\ln x)^2 dx.
\]
%\item
%Evaluate
%\[
%\int_1^2 \frac{ e^{1/x} }{x^2} dx.
%\]

\end{enumerate}

\end{document}
