\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate, verbatim, url}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Algebraic number theory (Spring 2013) -- Supplementary evaluations}
\end{center}
\begin{center}Frank Thorne, thorne@math.sc.edu
\end{center}

{\itshape Please offer your input on this semester's course, with particular attention to aspects which are
most under my control. In short -- please let me know what you would do differently next time, and what you would keep the same!

Some questions are listed below, but please ignore the questions if they don't reflect the feedback you would like to give.}

\begin{enumerate}
\item
Were the pace, and background assumed in the lectures a good match for your background?
If no, please explain.

\item
Did the topics covered correspond to what you would like to see? A couple topics we did cover that could have been
left out: the theory of valuations; the proofs of finiteness of the class number and the unit theorem. A couple topics we might
have covered instead: more about the connection to analytic number theory (Gauss sums, Tate's thesis, ...); more emphasis
on numerical examples; more on adeles and ideles, class field theory and the advanced reaches of the theory; more on the relation
to classical questions involving Diophantine equations and so on.

\item
We did not follow any textbook exactly, although we could have. Would it have been helpful to stick to a single source?

\item
Was the homework appropriately challenging, interesting, and did you feel prepared for it? Were there any types of questions you would
have liked to have seen more of?

\item
({\itshape Optional, but please consider answering if it doesn't make you uncomfortable.})
If you didn't do enough of the homework to earn an A, what was the obstacle?

If you had other priorities (e.g. finishing a thesis), or decided that you are not all that interested in algebraic number theory,
then that can't be helped. If neither of these is the case, your feedback will be very helpful next time I plan a similar course.
\end{enumerate}

\end{document}
