\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Homework 4 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{enumerate}[(a)]

\item
Draw a graph of a function which is not differentiable, and geometrically explain why it is not differentiable.

\item
Give an equation of a function which is not differentiable, and algebraically explain why it is not differentiable.
(You can use the same function or a different function.)

\item
Give the definition of the {\itshape derivative} of a function
$f(x)$ at the point $x = a$. (Please give the algebraic definition,
using an equation.)

Draw a picture and explain why your
equation gives the slope of the tangent line to the graph of $f(x)$
at $x = a$.

\item
Thomas, Ch. 3.2: 27-32.
\item
Thomas, Ch. 3.2: 7-10, 13-14, 19, 20, 23-26, 43-48. Even required; odd additional.
{\bf Instructions:} You may use the definition, the `alternative formula', and
any other techniques in this chapter at your discretion. Do not use the differentiation
rules introduced in later chapters.

\item
Thomas, Ch. 3.3: 17-34 (even required, odd additional), 57, 58.

\item
Thomas, Ch. 3.5: 1-14, 35-38 (even required, odd additional).

If $f(x) = c$, where $c$ is a constant, find $f'(x)$ using the definition.
Draw a picture which explains your conclusion.

\item
What is the 500th derivative of $f(x) = x^{100}$? Explain why.

\end{enumerate}

\end{document}
