\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Final Examination -- Math 531}
\end{center}
\begin{center}
{\bf Frank Thorne -- Saturday, December 15, 9:00 a.m.}
\end{center}

{\bf Proofs.}
\begin{enumerate}[(1)]
\item
Prove that the sum of angles of a triangle is 180 degrees (i.e., is the same as a straight line).
\item
In quadrilateral $ABCD$, suppose that $AB = CD$ and $AD = BC$. Prove that $ABCD$ is a parallelogram.
(In your proof, do not appeal to any facts about parallelograms other than the definition.)
\item
Prove that the arc subtended by an inscribed angle is equal to twice the angle.

You may, if you like,
restrict yourself to the special case depicted in Figure III.1: Prove that $\stackrel\frown{BC} = 2 \angle A$. Here $B$ and $C$ are on opposite sides of the diameter from $A$.
\item
In Figure III.2, the two circles meet at points $P$ and $Q$, and diameters $PA$ and $PB$ are drawn.
Show that line $AB$ goes through point $Q$.
\item
Prove that the three altitudes of a triangle are concurrent.
\item
Prove the following without using trigonometry: In triangle $\triangle ABC$, if side $AB$ is larger than
side $BC$, then angle $C$ is larger than angle $A$.

{\itshape Hint:} This was Proposition 18 of Euclid. If you remember the proposition that Euclid quoted,
feel free to do the same. If not, you might find it helpful to quote the fact that the angles of a triangle
add up to 180 degrees.
\item
In Figure III.3, we have chosen a point $X$ on the extension of diagonal $BD$ of square $ABCD$,
and we have dropped a perpendicular $CP$ from $C$ to $AX$. If $CP$ meets $DB$ at $Y$ and
$BY = XD$, show that $BY = BA$, either by the following procedure or otherwise:
\begin{enumerate}[(a)]
\item
Explain why $A$, $B$, $C$, $D$, and $P$ are all on the same circle.
\item
Use cross ratios to show that $\frac{XY \cdot BD}{XD \cdot BY} = 2$.
\item
Writing $DX = 1$ and $DY = x$, determine $x$ and then conclude.
\end{enumerate}
\item
Write out the following sentence twice, with four different words in the blanks that make
the sentence true. Then prove your claims. (A variety of correct answers are possible.)

\begin{center}
In triangle $\triangle ABC$, if the --------- and the ---------- are the same point, 
then $\triangle ABC$ is equilateral.
\end{center}

\end{enumerate}

\end{document}
