\documentclass[12pt]{article}
\textwidth 7.0in
\oddsidemargin -0.4in
\evensidemargin -0.4in
\textheight 9.0in 
\pagestyle{empty}
\usepackage{enumerate}
\begin{document}
% 8.5in paper width -2x1in margin = 6.5in text width
\setlength{\topmargin}{-2mm}



% 11in paper height -2x1in margin = 9in text height


\begin{center}{\bf Homework 6 - Math 141, Frank Thorne (thornef@mailbox.sc.edu)}
\end{center}
\begin{center}
{\bf Due Friday, October 12}
\end{center}
Required problems:
\begin{enumerate}[(a)]

\item
If $y = \ln x$, explain why $\frac{dy}{dx} = \frac{1}{x}$.

\item
Find $\frac{dy}{dx}$ if $y = \log_a x$.

\item
Explain why $e = \lim_{x \rightarrow 0} (1 + x)^{1/x}.$

\item
Explain why $e = \lim_{n \rightarrow \infty} \bigg(1 + \frac{1}{n} \bigg)^n.$

\item
Stewart, Ch. 3.6, 1.

\item
Stewart, Ch. 3.6, 3-14, 37-42 (even).

\item
Stewart, Ch. 3.6, 49, 50.

\item
Stewart, Ch. 3.7, 5, 6, 7, 10, 12(a), 20, 21.

\item
Explain what kind of situations are natural modeled by an exponential
decay law. Describe a general principle and give at least two examples.

\item
Explain the meaning and origin of the equation $y(t) = y(0) e^{kt}$.
When is $k$ positive, and when is it negative?

\item
What is a {\itshape differential equation}?

\item
Stewart, Ch. 3.8, 2, 8, 14, 18, 20.

\end{enumerate}
Additional problems:
\begin{enumerate}[(a)]
\item
Stewart, Ch. 3.6, 3-14, 37-42 (odd).

\item
Stewart, Ch. 3.7, 9, 14.

\item
Stewart, Ch. 3.8, 3, 9, 15.

\end{enumerate}
Bonus (2 points). Say you take out a 30-year 
{\bf mortgage} of \$100,000 at 5\%. This means that you pay
interest of 5\% on your debt, compounded continuously, and you make
a monthly payment at the end of each month.

The monthly payment is calculated so that (1) it is the same every 
month, and (2) it will take you exactly 360 payments to pay off 
your entire mortgage (including principal and interest).

Compute the monthly payment. You may need to 
use a computer or calculator, but fully explain what you are doing.


\end{document}
